\documentclass[11pt,a4paper]{article}

% ---- Packages ----
\usepackage[margin=1.8cm, top=1.6cm, bottom=1.6cm]{geometry} % Slightly adjusted for balance
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[scaled=0.95]{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}

% ---- Colors ----
\definecolor{accentcolor}{RGB}{25, 50, 120}
\definecolor{darkgray}{RGB}{70, 70, 70}

% ---- Setup ----
\hypersetup{
    colorlinks=true,
    urlcolor=accentcolor,
    linkcolor=accentcolor
}

\setlength{\parindent}{0pt}
\setstretch{1.04} % Subtle reduction in line height to save space globally

% Page numbering
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\color{accentcolor}\small Page \thepage\ of \pageref{LastPage}}

% ---- Custom Commands ----
\newcommand{\makeheader}[3]{
    \begin{center}
        {\Huge\bfseries\color{accentcolor} #1} \\[0.2em]
        {\Large\color{darkgray} #2} \\[0.4em]
        \small
        Email: \href{mailto:#3}{#3} \quad
        Web: \href{https://arifsolmaz.github.io}{arifsolmaz.github.io} \quad
        Tel: (+90) 538 614 29 38 \\[0.1em]
        Location: Istanbul, Turkey
    \end{center}
    \vspace{-1.0em}
}

\titleformat{\section}
  {\Large\bfseries\color{accentcolor}\uppercase}
  {}{0em}{}
  [\titlerule]
\titlespacing*{\section}{0pt}{10pt}{6pt} % Tightened section spacing

\newcommand{\cventry}[4]{
  \vspace{4pt}
  \textbf{#1} \hfill \textit{#3} \\
  \textbf{\color{darkgray} #2} \hfill #4 \\
}

\newcommand{\cvdesc}[1]{
  \vspace{-1pt}
  \begin{itemize}[leftmargin=12pt, nosep, label=\small\textbullet]
    \small #1
  \end{itemize}
}

\setlist[itemize]{leftmargin=*, labelsep=3mm, itemsep=2pt, topsep=1pt}

% ---- DOCUMENT START ----
\begin{document}

% ===================== HEADER =====================
\makeheader
    {Arif Solmaz, PhD}
    {Assistant Professor --- Exoplanet Science \& Scientific ML}
    {arif.solmaz@istun.edu.tr}

% ===================== PROFILE =====================
\section{Profile}
Astronomer specializing in exoplanet transit photometry and timing analysis, with emphasis on characterizing systematic effects from stellar activity. I develop Bayesian and machine learning pipelines to extract precise transit parameters from TESS, JWST, and ground-based data, specializing in transit timing variations (TTVs) and starspot-induced biases. As a lead contributor to international collaborations including the ExoClock Project and EXPLORE, I coordinate multi-site observing campaigns across 50+ countries. I teach computational methods and programming at the undergraduate level and maintain reproducible, open-source research workflows.

% ===================== EDUCATION =====================
\section{Education}

\cventry{PhD in Physics}{Çukurova University}{Jan 2023}{Adana, Turkey}
\cvdesc{
    \item Dissertation: \textit{Effects of Starspot Occultations on Exoplanet Transit Mid-time Measurements}
    \item Advisors: Prof.\ Dr.\ Aysun Akyüz \& Prof.\ Dr.\ Özgür Baştürk (Ankara University)
}

\cventry{MSc in Space Sciences and Technologies}{Çanakkale Onsekiz Mart University}{Oct 2010}{Çanakkale, Turkey}
\cvdesc{
    \item Thesis: \textit{Extrasolar Planetary Systems: a status review}
    \item Advisor: Prof.\ Dr.\ Mehmet Emin Özel
}

\cventry{BSc in Physics}{Çanakkale Onsekiz Mart University}{Jan 2008}{Çanakkale, Turkey}
\cvdesc{
    \item Advisor: Prof.\ Dr.\ Faruk Soydugan
}

% ===================== ACADEMIC APPOINTMENTS =====================
\section{Academic Appointments}

\cventry{Assistant Professor}{İstanbul Health and Technology University (İSTÜN)}{May 2024 -- Present}{Istanbul, Turkey}
Department of Mechatronics Engineering, Faculty of Engineering \& Natural Sciences. Teaching programming, data structures, and machine learning courses; leading research in exoplanet science and applied ML.

\cventry{Lecturer}{Çağ University, Faculty of Arts and Sciences}{Sep 2015 -- Jun 2023}{Mersin, Turkey}
Taught statistics, programming, and quantitative methods while completing PhD in parallel. Developed digital learning materials and supervised student projects.

\cventry{Research Assistant}{Çağ University, Faculty of Arts and Sciences}{Feb 2011 -- Sep 2015}{Mersin, Turkey}
Supported teaching and observational research activities; contributed to TÜBİTAK-funded meteor monitoring and stellar astrophysics programs.

% ===================== PUBLICATIONS =====================
\section{Selected Publications}

\textit{Complete list at \href{https://arifsolmaz.github.io}{arifsolmaz.github.io}.}

\vspace{0.2em}
\textbf{Peer-Reviewed Journal Articles:}
\begin{itemize}
\item \href{https://doi.org/10.1051/0004-6361/202556498}{A high geometric albedo and small size for the Haumea cluster member (24835) 1995 SM55 determined from a stellar occultation and photometric observations}. \textit{Astronomy \& Astrophysics}, 703, A147, 2025

\item \href{https://doi.org/10.1093/mnras/staf1659}{Testing the performance of cross-correlation techniques to search for molecular features in JWST NIRSpec G395H observations of transiting exoplanets}. \textit{MNRAS}, 543, 3456, 2025

\item \href{https://ui.adsabs.harvard.edu/abs/2025arXiv251114407K/abstract}{ExoClock Project IV: A homogeneous catalogue of 620 updated exoplanet ephemerides}. \textit{ApJS}, 283, 5, 2026 $\cdot$ 100+ authors

\item \href{https://doi.org/10.3847/1538-4365/ac9da4}{ExoClock Project III: 450 New Exoplanet Ephemerides from Ground and Space Observations}. \textit{ApJS}, 265, 4, 2023 $\cdot$ 60+ authors

\item \href{https://doi.org/10.55064/tjaa.1203704}{Leke Örtülmelerinin Ötegezegen Geçiş Ortası Zaman Ölçümlerine Etkisi}. \textit{Turkish Journal of Astronomy and Astrophysics}, 4, 147, 2023

\item \href{https://doi.org/10.1051/0004-6361/202141546}{Physical properties of the trans-Neptunian object (38628) Huya from a multi-chord stellar occultation}. \textit{A\&A}, 664, A130, 2022

\item \href{https://doi.org/10.1016/j.newast.2021.101571}{BO Ari Light Curve Analysis using Ground-Based and TESS Data}. \textit{New Astronomy}, 86, 101571, 2021

\item \href{https://doi.org/10.1134/S1063773721060050}{The First Light Curve Solutions and Period Study of BQ Ari}. \textit{Astronomy Letters}, 47, 402, 2021
\end{itemize}

\vspace{0.2em}
\textbf{Selected Conference Contributions:}
\begin{itemize}
\item \href{https://doi.org/10.5194/epsc-dps2025-1467}{Artificial Intelligence in Planetary Science and Astronomy: Applications and Research Potential}. EPSC-DPS Joint Meeting 2025 $\cdot$ Invited presentation

\item \href{https://doi.org/10.5194/epsc-dps2025-1815}{Europlanet Machine Learning Working Group: a year of progress}. EPSC-DPS Joint Meeting 2025
\end{itemize}

% ===================== FUNDED PROJECTS =====================
\section{Funded Projects}

\textbf{As Principal Investigator / Coordinator:}
\begin{itemize}
    \item \textbf{Geometric Modeling and Analysis of Exoplanet Transit Observations} --- University Scientific Research Project. \textit{2019--2020.}\\
    Bayesian parameter estimation from transit photometry; handling stellar activity systematics.

    \item \textbf{MILAGE: Technology Use in Mathematics Education} --- EU Erasmus+ Programme. \textit{2015--2018.}\\
    Coordinated multi-country partnership on digital tools in education.

    \item \textbf{Turkey Meteor Monitoring Systems and Network (Continuation)} --- University Scientific Research Project. \textit{2019--2020.}

    \item \textbf{Light Pollution Measurement Studies} --- University Scientific Research Project. \textit{2019--2020.}
\end{itemize}

\textbf{As Team Member:}
\begin{itemize}
    \item \textbf{The Impact of Non-Markovian Memory Effects on the Learning Dynamics of Quantum Neural Networks} --- TÜBİTAK. \textit{Submitted / Under Review.}\\
    Investigation of non-Markovianity and memory effects in the optimization and training trajectories of quantum machine learning models.

    \item \textbf{ML-Based Microscopic Wood Species Identification System} --- TÜBİTAK-1002. \textit{Ongoing.}\\
    Deep learning models for automated classification from microscopic images.

    \item \textbf{Turkey Meteor Monitoring Systems and Network: National Impact Craters and Meteorites Database} --- TÜBİTAK-1001. \textit{2014--2017.}

    \item \textbf{Multi-faceted Analyses of Binary and Multiple Star Systems} --- TÜBİTAK-1010 EVRENA. \textit{2010--2013.}
\end{itemize}

% ===================== SOFTWARE =====================
\section{Software \& Tools}
\begin{itemize}
    \item \textbf{\href{https://github.com/ArifSolmaz}{TransitKit}}: Python toolkit for exoplanet transit light curve analysis --- Bayesian fitting, MCMC sampling, systematic detrending, publication-quality output
    \item \textbf{\href{https://arifsolmaz.github.io/arxiv}{arXiv Monitor}}: Automated daily aggregator for exoplanet literature with AI-generated summaries (\href{https://github.com/ArifSolmaz/arifsolmaz.github.io}{source})
\end{itemize}

% ===================== SKILLS =====================
\section{Technical Skills}
\begin{itemize}
    \item \textbf{Programming}: Python, C, Bash; Git/GitHub; Linux environments
    \item \textbf{Scientific Stack}: NumPy, SciPy, Pandas, Matplotlib; Astropy, Photutils, Lightkurve
    \item \textbf{Statistics \& ML}: Bayesian modeling, MCMC (emcee, PyMC), Gaussian processes (celerite); Scikit-learn, TensorFlow/Keras; CNNs, transfer learning
    \item \textbf{Other}: LaTeX, Jupyter; Turkish (native), English (advanced --- YÖKDİL 87.5/100)
\end{itemize}

% ===================== COLLABORATION & SERVICE =====================
\section{Collaboration \& Service}
\begin{itemize}
    \item \textbf{ExoClock Collaboration}: Ground-based observation coordination and ephemeris refinement; 100+ observers, 50+ countries; supporting ESA Ariel mission scheduling
    \item \textbf{EXPLORE Project}: International TTV observing campaign; contributing photometric data and analysis to the AAVSO Exoplanet Database pipeline
    \item \textbf{Europlanet ML Working Group}: Coordinating community efforts in AI/ML applications for planetary science
    \item \textbf{Multi-Site Stellar Occultation Campaigns}: Data analysis and coordination for physical characterization of trans-Neptunian objects
    \item \textbf{Peer Review}: Referee for international astronomy and planetary science journals
\end{itemize}

% ===================== TEACHING =====================
\section{Teaching}

\textbf{Current (2024--2025, İSTÜN):} Physics I \& II, Computer Programming I \& II, Object-Oriented Programming, Data Structures \& Algorithms, Robotics, Machine Learning --- all in English and/or Turkish.

\vspace{2pt}
\textbf{Previous (Çağ University):} Statistics, Quantitative Methods, Introductory--Advanced Programming.

% ===================== OUTREACH =====================
\section{Outreach \& Leadership}
\begin{itemize}
    \item \textbf{ESO Science Outreach Network}, Turkey Contact Point \hfill \textit{2010--2022}
    \item \textbf{Universe Awareness (UNAWE)}, Turkey Representative \hfill \textit{2011--2015}
    \item \textbf{BAP Coordinator}, Çağ University Research Projects Unit \hfill \textit{2020--2021}
    \item \textbf{Executive Board}, Çağ University Observatory (UZAYMER) \hfill \textit{2012--2023}
    \item Multiple TÜBİTAK-funded science communication projects \hfill \textit{2018--2021}
\end{itemize}

% ===================== MEMBERSHIPS =====================
\section{Professional Memberships}
International Astronomical Union (IAU), European Astronomical Society (EAS), Turkish Astronomical Society (TAD), European Association for Astronomy Education (EAAE --- Board Member).

\vspace{0.6em}
\begin{center}
\hrule
\vspace{0.4em}
\small\textit{Complete publication list, research code, and teaching materials at \href{https://arifsolmaz.github.io}{arifsolmaz.github.io}.
References available upon request.}
\end{center}

\end{document}
